The globular cluster system of the Auriga simulations

### 2019-08-19 AurigaGCS.tex
Edited Sec. 2 (Auriga) based on feedback WHT, RG, FM for #1.

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}    % per cm-squared
\newcommand{\Sun}[0]{\ensuremath{_{\odot}}}
\renewcommand{\deg}{\ensuremath{^{\circ}}}

@@

In this work we use state of the art simulations that produce realistic spiral 
galaxies (Milky Way analogues) at redshift zero for which several global properties 
are consistent with the observations. The question thus naturally arises whether 
the star formation histories of the simulations give rise to a GC system 
similar to the Milky Way and/or Andromeda globular cluster systems. In particular, 
we use the Auriga suite of cosmological zoom simulations 
(\citealt{2017MNRAS.467..179G}, and described in Sec.~\ref{sec:auriga}) to
investigate whether the star formation model implemented produces metallicity, 
radial, and metallicity-radial distributions that are consistent with the MW 
and/or M31 GC systems, and whether the model produces enough stellar mass with
the right properties to allow for formation efficiencies lower than unity and
the expected (dynamical) mass loss over the cluster lifetime (not modelled 
explicitly in this study).

@@

\section{The Auriga simulations}
\label{sec:auriga}
We use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, a
suite of high-resolution cosmological zoom simulations of Milky Way-mass
selected initial conditions. The simulations are performed with the \textsc{arepo} 
\citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} code that solves the 
magnetohydrodynamical equations on a moving mesh. The galaxy formation model 
produces realistic spiral galaxies at redshift $z=0$.

The interstellar medium is modelled using a sub-grid approach which implements
the physical processes most relevant to galaxy formation and evolution.
This model was tailored to the \textsc{arepo} code and calibrated to reproduce
key observables of galaxies, such as the history of the cosmic star formation rate
density, the stellar mass to halo mass relation, and galaxy luminosity functions.

The sub-grid includes primordial and metal-line cooling with self-shielding
corrections. Reionization is completed at redshift six by a time-varying
spatially uniform UV background \citep{2009ApJ...703.1416F, 2013MNRAS.436.3031V}.
The interstellar medium is described by an equation of state for a two-phase medium
in pressure equilibrium \citep{2003MNRAS.339..289S} with stochastic star formation
in thermally unstable gas with a density threshold of $n = 0.13 \text{cm}^{-3}$,
and consecutive stellar evolution is accounted for. Stars provide feedback by
stellar winds \citep{2014MNRAS.437.1750M, 2017MNRAS.467..179G}, and further
enrich the ISM with metals from SNIa, SNII, and AGB stars \citep{2013MNRAS.436.3031V}.
The formation of black holes is modelled which results in feedback from active
galactic nuclei \citep{2005MNRAS.361..776S, 2014MNRAS.437.1750M, 2017MNRAS.467..179G}.
Finally, the simulations follow the evolution of a magnetic field of $10^{-14}$
(comoving)~G seeded at $z = 127$ \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}.
See G17 for further details of the numerical setup as well as the galaxy formation
model.

The Auriga suite has a fiducial resolution level L4, accompanied by the lower
(higher) level L5 (L3) that is available for selected initial condition runs.
The baryonic mass resolution in order of increasing level is $m_b$~=~[$4 \times 10^5$,
$5 \times 10^4$, $6 \times 10^3$]~M\Sun \, with gravitational softening of
collissionless particles $\epsilon$~=~[$738, 369, 184$]~pc. The mass resolution
of the Auriga simulations is thus close to the characteristic peak mass of the
lognormal GC mass distribution of $10^{5}$~M\Sun \citep{1991ARA&A..29..543H},
although the gravitational softening is two orders of magnitudes larger than
typical GC radii. High-density gaseous regions are thus not expected to produce
surviving stellar clumps with masses and radii consistent with GCs because
such objects would numerically disperse, even in the highest-resolution runs.
On the other hand, we can investigate (statistical) properties of age-selected
GC candidates because each star particle represents a single stellar population
with a total mass that could be consistent with one globular cluster. This means
that their formation sites and that of a real-world GC may be consistent.

@@

\section{Discussion}
% ``The Auriga Stellar Haloes: Connecting stellar population properties with
% accretion and merging history'' \citet{2018arXiv180407798M}

\label{sec:discussion}
\subsection{Metallicity distribution}
\label{sec:discussion_FeH}
Globular clusters are ${\sim}0.5$ dex more metal-poor than spheroid stars observed 
at the same radius for almost all galaxies \citep{1991ARA&A..29..543H}. Our 
selection function (age cut) does lower the mean metallicity by $0.5$ dex, but
we still find that the metallicity distributions of GC candidates in the Auriga
simulations are more metal-rich than the MW (M31) GCS. Although the (old) star
particles represent single stellar populations with a mass (resolution) consistent 
with that of GCs, they are in fact statistical tracers of the stellar population 
of the galaxy as a whole. Therefore only a (small) fraction of the star particles 
may represent plausible formation sites of GCs, whereas the majority represents 
(halo) field stars - the disk component effectively falls outside our selection 
of star particles due to the age cut. It is implausible that all halo stars 
come from disrupted GCs because GC systems that survive down to redshift zero 
are generally few orders of magnitude less massive than galactic stellar haloes.

>>>>

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}    % per cm-squared
\newcommand{\Sun}[0]{\ensuremath{_{\odot}}}
\renewcommand{\deg}{\ensuremath{^{\circ}}}
\defcitealias{2017MNRAS.467..179G}{G17}

@@

In this work we use state of the art simulations that produce realistic spiral 
galaxies (Milky Way analogues) at redshift zero for which several global properties 
are consistent with the observations. The question thus naturally arises whether 
the star formation histories of the simulations give rise to a GC system 
similar to the Milky Way and/or Andromeda globular cluster systems. In particular, 
we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
further described in Sec.~\ref{sec:auriga}. We investigate whether the star 
formation model implemented produces metallicity, 
radial, and metallicity-radial distributions that are consistent with the MW 
and/or M31 GC systems, and whether the model produces enough stellar mass with
the right properties to allow for formation efficiencies lower than unity and
the expected (dynamical) mass loss over the cluster lifetime (not modelled 
explicitly in this study).

@@

\section{The Auriga simulations}
\label{sec:auriga}
We use the Auriga simulations \citepalias{2017MNRAS.467..179G}, a suite of 
high-resolution cosmological zoom simulations. The Milky Way-mass
selected initial conditions were selected from the \mbox{\textsc{eagle}} DM only 
box, see \citetalias{2017MNRAS.467..179G} for details. The simulations are performed with the \textsc{arepo} 
code \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} that solves the 
magnetohydrodynamical equations on a moving mesh.

The galaxy formation model includes primordial and metal-line cooling with 
self-shielding corrections. Reionization is completed at redshift six by a
time-varying spatially uniform UV background \citep{2009ApJ...703.1416F, 
2013MNRAS.436.3031V}. The interstellar medium (ISM) is described by an equation of 
state for a two-phase medium in pressure equilibrium \citep{2003MNRAS.339..289S}: 
cold clouds embedded in a hot ambient medium, whose mass and energy densities
are described by processes important for star formation, such as the condensation 
of cold clouds and the photoevaporation of clouds. Stars form stocastically in 
thermally unstable gas with a density threshold of $n = 0.13 \, \text{cm}^{-3}$,
and consecutive stellar evolution is accounted for. The channel for energetic
stellar feedback is from non-local SNII, which is modelled with wind particles
(\citealt{2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}). Galactic 
winds enrich the ISM
with metals from SNIa, SNII, and AGB stars \citep{2013MNRAS.436.3031V}. Supermassive
black holes grow via Bondi–Hoyle–Lyttleton accretion \citep{1944MNRAS.104..273B,
1952MNRAS.112..195B}, and feedback from the active galactic nuclei has a low-accretion
and high-accretion mode (radio and quasar) (\citealt{2005MNRAS.361..776S, 
2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}). Finally, the simulations 
follow the evolution of a magnetic field of $10^{-14}$ (comoving)~G seeded at 
$z = 127$ \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}.

This model was tailored to the \textsc{arepo} code and calibrated to reproduce
key observables of galaxies, such as the history of the cosmic star formation rate
density, the stellar mass to halo mass relation, and galaxy luminosity functions.
The galaxy formation model produces realistic spiral galaxies at redshift $z=0$.
Moreover, Auriga reproduces the HI disc properties \citep{2017MNRAS.466.3859M},
the chemical thin/thick disc \citep{2018MNRAS.474.3629G}, the diversity in 
accreted stellar halo properties found in observations \citep{2019MNRAS.485.2589M},
and the \textit{Gaia} Sausage \citep{2019MNRAS.484.4471F}. These last two 
bolster the point that the simulations are similar (and detailed) enough to the 
MW to reproduce major, distinct features of the Galaxy, and so looking for the 
GC population properties and comparing them to the MW/M31 is all the more relevant.

The Auriga suite has a fiducial baryonic mass resolution $m_b$~=~$5 \times 10^4$~M\Sun,
with gravitational softening of collissionless particles $\epsilon$~=~369~pc.
Simulations at this resolution are referred to as level 4 (L4). Selected
initial condition runs are acompanied by the lower (higher) resolution level L5 (L3).
The resolution for these levels is $m_b$~=~$4 \times 10^5$~M\Sun \, with 
$\epsilon$~=~738~pc, and $m_b$~=~$6 \times 10^3$~M\Sun \, with $\epsilon$~=~184~pc,
respectively. The mass resolution of the Auriga simulations is thus close to the 
characteristic peak mass of the lognormal GC mass distribution of $10^{5}$~M\Sun 
\citep{1991ARA&A..29..543H}, although the gravitational softening is two orders 
of magnitudes larger than typical GC radii of several parsec. High-density gaseous 
regions are thus not expected to produce surviving stellar clumps with masses and 
radii consistent with GCs because such objects would numerically disperse, even 
in the highest-resolution runs. On the other hand, we can investigate (statistical) 
properties of age-selected GC candidates because each star particle represents a
single stellar population with a total mass that could be consistent with one 
globular cluster. This means that their formation sites and that of a real-world 
GC may be consistent.

@@

\section{Discussion}
\label{sec:discussion}
\subsection{Metallicity distribution}
\label{sec:discussion_FeH}
Globular clusters are ${\sim}0.5$ dex more metal-poor than spheroid stars observed 
at the same radius for almost all galaxies \citep{1991ARA&A..29..543H}. Our 
selection function (age cut) does lower the mean metallicity by $0.5$ dex, but
we still find that the metallicity distributions of GC candidates in the Auriga
simulations are more metal-rich than the MW (M31) GCS. Although the (old) star
particles represent single stellar populations with a mass (resolution) consistent 
with that of GCs, they are in fact statistical tracers of the stellar population 
of the galaxy as a whole. Therefore only a (small) fraction of the star particles 
may represent plausible formation sites of GCs, whereas the majority represents 
(halo) field stars - the disk component effectively falls outside our selection 
of star particles due to the age cut. It is implausible that all halo stars 
come from disrupted GCs because GC systems that survive down to redshift zero 
are generally few orders of magnitude less massive than galactic stellar haloes.
